PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.

### 2024-03-06 docs/_tex/index.tex
short disc

The primary objective of this study was to develop a method for the
accurate classification of macrophytes on intertidal mudflats,
specifically focusing on distinguishing between Chlorophyceae (green
algae) and marine Magnoliopsida (seagrasses) using multispectral drone
data. The challenge arises from the shared pigment composition between
these two vegetation classes, complicating their differentiation using
remote sensing techniques. This challenge has been addressed through the
utilization of high-resolution drone flights allowing a precise
photointerpretation of pure pixels of the different vegetation classes
used as training data, providing a robust foundation for subsequent
classification analyses. In achieving 94.26 accuracy across all study
sites, this method demonstrates its efficacy in accurately classifying
macrophytes, thus offering a reliable approach for vegetation
classification in intertidal mudflats using remote sensing data.

@@

The discrimination of seagrasses from green macroalgae presents
significant challenges, primarily due to the shared pigment composition
between these taxa, as depicted in Figure~\ref{fig-Pigm} but also by the
frequent spatial mixing of these green macrophytes. This similarity in
pigment composition, including photosynthetic and carotenoid pigments
like chlorophyll b and c, fucoxanthin, and neoxanthin, results in
spectral signatures that are often indistinguishable to non exper eyes.
This spectral overlap is further complicated by the intermingling of
seagrasses and green macroalgae in the same spatial locations, posing a
significant challenge for remote sensing aimed at accurately mapping and
monitoring coastal ecosystems. Our study addresses these complexities by
utilizing high-resolution drone imagery with 10 spectral bands.
\citep{Davies2023} has shown that having at least 8 spectral bands
ranging between 500 nm to 850 nm with including a band at 530 nm and
another one at 730 nm is crucial to accurately discriminate green
macrophytes.

>>>>

@@

The primary objective of this study was to develop a method for the
accurate classification of macrophytes on intertidal mudflats,
specifically focusing on distinguishing between Chlorophyceae (green
algae) and marine Magnoliopsida (seagrasses) using multispectral drone
data. The discrimination of seagrasses from green macroalgae presents
significant challenges, primarily due to the shared pigment composition
between these taxa, as depicted in Figure~\ref{fig-Pigm} but also by the
frequent spatial mixing of these green macrophytes. This similarity in
pigment composition, including photosynthetic and carotenoid pigments
like chlorophyll b and c, fucoxanthin, and neoxanthin, results in
spectral signatures that are often indistinguishable to non exper eyes.
This spectral overlap is further complicated by the intermingling of
seagrasses and green macroalgae in the same spatial locations, posing a
significant challenge for remote sensing aimed at accurately mapping and
monitoring coastal ecosystems. Our study addresses these complexities by
utilizing high-resolution drone imagery with 10 spectral bands.
\citep{Davies2023} has shown that having at least 8 spectral bands
ranging between 500 nm to 850 nm with including a band at 530 nm and
another one at 730 nm is crucial to accurately discriminate green
macrophytes.

### 2024-03-06 index.qmd
short disc

# Discussion

The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green algae) and marine Magnoliopsida (seagrasses) using multispectral drone data. The challenge arises from the shared pigment composition between these two vegetation classes, complicating their differentiation using remote sensing techniques. This challenge has been addressed through the utilization of high-resolution drone flights allowing a precise photointerpretation of pure pixels of the different vegetation classes used as training data, providing a robust foundation for subsequent classification analyses. In achieving `r round(validation_metrics$overall[[1]]*100,2)` accuracy across all study sites, this method demonstrates its efficacy in accurately classifying macrophytes, thus offering a reliable approach for vegetation classification in intertidal mudflats using remote sensing data.

## Vegetation Discrimination

@@

The discrimination of seagrasses from green macroalgae presents significant challenges, primarily due to the shared pigment composition between these taxa, as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes. This similarity in pigment composition, including photosynthetic and carotenoid pigments like chlorophyll b and c, fucoxanthin, and neoxanthin, results in spectral signatures that are often indistinguishable to non exper eyes. This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems. Our study addresses these complexities by utilizing high-resolution drone imagery with 10 spectral bands. @Davies2023 has shown that having at least 8 spectral bands ranging between 500 nm to 850 nm with including a band at 530 nm and another one at 730 nm is crucial to accurately discriminate green macrophytes.

>>>>

# Discussion
## Vegetation Discrimination

@@

The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green algae) and marine Magnoliopsida (seagrasses) using multispectral drone data. The discrimination of seagrasses from green macroalgae presents significant challenges, primarily due to the shared pigment composition between these taxa, as depicted in @fig-Pigm but also by the frequent spatial mixing of these green macrophytes. This similarity in pigment composition, including photosynthetic and carotenoid pigments like chlorophyll b and c, fucoxanthin, and neoxanthin, results in spectral signatures that are often indistinguishable to non exper eyes. This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems. Our study addresses these complexities by utilizing high-resolution drone imagery with 10 spectral bands. @Davies2023 has shown that having at least 8 spectral bands ranging between 500 nm to 850 nm with including a band at 530 nm and another one at 730 nm is crucial to accurately discriminate green macrophytes.
